\papertitle

### 2021-03-11 source_separation/paper/paper.tex
Final edits

	For example, consider an example target that has a continuous drone sound throughout and a melody playing above this drone. Without source separation, Orchidea would detect each note of the melody as a new onset and cut the target in time at each new note. However, this segmentation in time would also effect the drone, cutting it in time and forcing it to have a new onset each time the melody changes notes. The resulting orchestration would have multiple onsets for the drone, when really only one onset is needed at the beginning of the drone. When source separation is applied to this target, the drone and melody would be orchestrated separately. Therefore, the drone could be orchestrated by a single onset that lasts for the duration of the drone. At the same time, the melody could have as many new onsets as needed without affecting the drone. The orchestration would be greatly improved by removing the unnecessary onsets in the orchestration of the drone. This is the effect we achieve through implementing source separation in computer-assisted orchestration.

@@

		The procedure we used for testing is as follows:
		\begin{enumerate}
			\item The target is created as a combination of four randomly chosen sources, which are offset to begin playing at different times
			\item The full target, without any separation performed, is orchestrated using the entire orchestra
			\item Each separation method is performed on the target, each splitting the target into 4 sub-targets 
			\item The full orchestra is randomly split into four equal sized subsets
			\item For each method, the four sub-targets are separately orchestrated, each using a different subset of the orchestra, and then each orchestration is combined to play simultaneously
			\item The ground truth orchestration is created by orchestrating the four sources, using the same orchestra splits from step 4, and then combined to play simultaneously
			\item The distances between target and orchestration are calculated for the full target orchestration, the separated orchestration, and the ground truth orchestration 
		\end{enumerate}

@@

		The distance metric cuts the target and solution into successive frames that are 4,000 samples in length, then calculates the spectral distance, as defined in Eqn. \ref{eqn:distance}, between corresponding frames. The spectral distance metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization, and used in \cite{Cella2020b} to compare accuracies of orchestrations. The equation takes in the full FFT of the target $x$ and full FFT of the solution $\tilde{x}$. Then for each bin $k$ of the FFT, it calculates the absolute difference between the values. The differing values of $\lambda_1$ and $\lambda_2$ allow the metric to penalize the solution in different ways. For our purposes, we used $\lambda_1 = 0.5$ and $\lambda_2 = 10$, which penalizes a solution that overshoots the harmonic energy of the target.

@@

		Another aspect we would like to work on is the assignment of the orchestras. Currently, the subset of the orchestra that is assigned to each sub-target is randomly selected. However, it is possible that this random assignment could reduce the quality of the final orchestration. If, for example, one of the sub-targets contains mostly low pitch content, but the orchestra assigned to it contains mostly violins, violas, flutes, and oboes, the resulting orchestration will suffer. To solve this problem, a step could be added that jointly-optimizes the the orchestras assigned to each sub-target, ultimately choosing an assignment that leads to the best orchestration of each sub-target.

>>>>

	For example, consider a target that has a continuous drone sound throughout and a melody playing above this drone. Without source separation, Orchidea would detect each note of the melody as a new onset and cut the target in time at each new note. However, this segmentation in time would also effect the drone, cutting it in time and forcing it to have a new onset each time the melody changes notes. The resulting orchestration would have multiple onsets for the drone, even though only one onset is needed at the beginning of the drone. When source separation is applied to this target, the drone and melody would be orchestrated separately. Therefore, the drone could be orchestrated by a single onset that lasts for the duration of the drone. At the same time, the melody could have as many new onsets as needed without affecting the drone. The orchestration would be greatly improved by removing the unnecessary onsets in the orchestration of the drone. This is the effect we achieve through implementing source separation in computer-assisted orchestration.

@@

		The procedure we used for testing is as follows:
		\begin{enumerate}
			\item The target is created as a combination of four randomly chosen sources, which are offset to begin playing at different times
			\item The full target, without any separation performed, is orchestrated using the entire orchestra
			\item Each separation method is performed on the target, each splitting the target into four sub-targets 
			\item The full orchestra is randomly split into four equal sized subsets
			\item For each method, the four sub-targets are separately orchestrated, each using a different subset of the orchestra, and then each orchestration is combined to play simultaneously
			\item The ground truth orchestration is created by orchestrating the four sources, using the same orchestra splits from step 4, and then combined to play simultaneously
			\item The distances between target and orchestration are calculated for the full target orchestration, the separated orchestration, and the ground truth orchestration 
		\end{enumerate}

@@

		The distance metric cuts the target and solution into successive frames that are 4,000 samples in length, which is approximately 90 milliseconds at a sampling rate of 44.1 kHz. The spectral distance, as defined in Eqn. \ref{eqn:distance}, is calculated between corresponding frames of the target and solution. The spectral distance metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization, and used in \cite{Cella2020b} to compare accuracies of orchestrations. The equation takes in the full FFT of the target $x$ and full FFT of the solution $\tilde{x}$. Then for each bin $k$ of the FFT, it calculates the absolute difference between the values. The differing values of $\lambda_1$ and $\lambda_2$ allow the metric to penalize the solution in different ways. For our purposes, we used $\lambda_1 = 0.5$ and $\lambda_2 = 10$, which penalizes a solution that overshoots the harmonic energy of the target.

@@

		Another aspect we would like to work on is the assignment of the orchestras. Currently, the subset of the orchestra that is assigned to each sub-target is randomly selected. However, it is possible that this random assignment could reduce the quality of the final orchestration. If, for example, one of the sub-targets contains mostly low pitch content, but the orchestra assigned to it contains mostly violins, violas, flutes, and oboes, the resulting orchestration will suffer. To solve this problem, a step could be added that jointly-optimizes the orchestras assigned to each sub-target, ultimately choosing an assignment that leads to the best orchestration of each sub-target.
